Differences in Homicide Case Information Indicates Why Justice is Not Served

### 2024-12-15 paper/paper.qmd
Updated paper qmd and pdf
Fixed formatting in paper

In our model, we assumed there is a relationship between the outcome variable, homicide is unsolved, with homicide case information like demographic (sex, race, and age of victim), geographic (city), and temporal (year) information, which are the predictor variables. For the demographic data, we decided to keep the grouping provided by The Washington Post such as "female" and "male" for the victim's sex and "White", "Black", "Hispanic", "Asian", and "Other for the victim's race. However, we did remove victims who have any demographic information that fall under the "Unknown" grouping from our dataset and did not run our regression model on these observations. The reason for this is due to factors such as the data type of our predictors and keeping consistency across all observations by removing any unknown values. For example, our predictor variable, victim's age is a integer data type but it contained the string "Unknown" in the raw dataset. So the values containing "Unknown" are removed from our final dataset and not used to train our model. Since our outcome variable is binary for our model, we constructed the arrest_was_not_made column for it based on the disposition variable to indicate if an arrest was made or not or in order words, the homicide is solved or unsolved. We considered dispositions with values like "Open/No arrest" and "Closed without arrest" to be 1 and "Closed by arrest" to be 0 for the arrest_was_not_made column.

@@

The purpose of these questions is to gauge the respondents' personal background. Questions that would be asked includes their email and information about their age, gender, ranking on the team, and educational attainment.

>>>>

In our model, we assumed there is a relationship between the outcome variable, homicide is unsolved, with homicide case information like demographic (sex, race, and age of victim), geographic (city), and temporal (year) information, which are the predictor variables. For the demographic data, we decided to keep the grouping provided by The Washington Post such as "female" and "male" for the victim's sex and "White", "Black", "Hispanic", "Asian", and "Other" for the victim's race. However, we removed victims who had any demographic information with the "Unknown" value from our dataset and did not run our regression model on these observations. The reason for this is due to factors such as the data type of our predictors and keeping consistency across all observations by removing any unknown values. For example, our predictor variable, victim's age is a integer data type but it contained the string "Unknown" in the raw dataset. So the values containing "Unknown" are removed from our final dataset and not used to train our model. Since our outcome variable is binary for our model, we constructed the arrest_was_not_made column for it based on the disposition variable to indicate if an arrest was made or not or in order words, the homicide is solved or unsolved. We considered dispositions with values like "Open/No arrest" and "Closed without arrest" to be 1 and "Closed by arrest" to be 0 for the arrest_was_not_made column.

@@

The purpose of these questions is to gauge the respondents' personal background. Questions that would be asked include their email and information about their age, gender, ranking on the team, and educational attainment.
